Convective penetration probably parameterizes convective overshoot

### 2021-07-10 manuscript/ms.tex
paper draft basically exists. Need to comb through it.

\subsection{Numerics}
We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008} and safety factor 0.35.
All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
The aspect ratio of our domains is two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure*}

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$2.5 million cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution (see appendix \ref{app:accelerated_evolution} for details) for the bulk of the simulations in this work.

The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries \citep[as studied in e.g.,][]{horst_etal_2021}.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state.
We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
On the right, we see that hot upwellings in the convective dynamics are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.

\subsection{Dependence on $\mP$}

We find that the depth of the penetration zone is strongly dependent on $\mP$.
In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (See e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution}).
At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.

In the middle and bottom panels of Fig.~\ref{fig:parameters_vs_p}, we plot average values of $f$ (middle panels) and $\xi$ (bottom panels) from our theory.
These values are respectively defined in Eqns.~\ref{eqn:f_defn} \& \ref{eqn:xi_defn}.
We find that $f$ has slightly smaller values in the discontinuous-$k$ simulations (left) than in the discontinuous-$\partial_z k$ simulations (right).
We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
In general we find a trend in which $f$ and $\xi$ are weakly inversely proportional to $\mP$ in some way.
This likely relates to the changing nature of the PZ as a function of $\mP$.
When $\mP \ll 1$, $\delp \rightarrow 0$ and the PZ is essentially an abrupt boundary layer at the top of the CZ.
Convective motions run into an abrupt wall and fall off sharply, leading to higher values of $\xi$.
This wall-like nature of the PZ pushes flows sideways and we find that the changes in $f$ can largely be explained by increased velocities within the CZ as $\mP$ decreases.
In the case whree $\mP \gg 1$, $\delp$ becomes large and the PZ becomes similar in nature to the one shown in Fig.~\ref{fig:vertical_dynamics_panels}.
Here the PZ acts as a large extension of the convection zone in which convective motions slowly brake under their own buoyancy.
$\xi$ decreases in value as the dissipation profile falls off smoothly with height and $f$ decreases in value as the dynamics in the PZ become dominated by dissipation.
(TODO: think about this more)

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{parameters_vs_p.pdf}
\caption{
Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (Left, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (Right, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}).
The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
The discontinuous penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
The discontinuous-gradient penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
We generally find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration depths.
In the bottom panels, we measure the evolved values of $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
\label{fig:parameters_vs_p}
}
\end{figure*}

@@

We find that the depth of the penetration zone is weakly dependent on $\mS$.
In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ becomes smaller.
To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.

We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$.

@@

We find that the depth of the penetration zone is weakly dependent on $\mR$.
In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth $\delta_{0.5}$ with the Reynolds number.
In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
We find that $f$ increases with increases $\mR$, but is perhaps leveling off.
We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
Indeed, we see in the bottom left panel that this variation of $\delp$ with $\mR$ can equally be seen as a variation of $\delp$ with $f$.
We find that this is true both for simulations with stress-free lower boundary (open symbols, SF) and for no-slip lower boundaries (closed symbols, NS).

In order to understand this better, we note that, at least in the SF simulations, the dissipation can roughly be modeled as a constant value in the CZ and zero in the viscous boundary layer (in the NS case, the dissipation becomes a maximum in the boundary layer).
This means that we can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
\begin{equation}
\int \bar{\Phi} dz = C ( L_s - \delta_\nu ),
\end{equation}
where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
In other words, under this model, we expect the dissipation, and thus $f$, to vary linearly with the viscous boundary layer depth.
Indeed, we find this to roughly be the case for the stress-free simulations in the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}.
We find that the NS simulations show a more complex increase as $\delta_\nu \rightarrow 0$ due to the fact that dissipation is maximized in the boundary layer and its magnitude there varies with $\mR$.
Regardless, we find that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection \citep{ahlers_etal_2009, goluskin2016}, as shown in the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, and so we anticipate that the value of $f$ should saturate as $\mR$ increases into the astrophysical regime.

Unfortunately, we are limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}), so we cannot extend our study to more turbulent simulations and higher values of $\mR$ than the ones shown here.
We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- give us hope that PZ depths should saturate at high $\mR$.

@@

\section{Accelerated Evolution}
\label{app:accelerated_evolution}
As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure can be done accurately.
This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
This same separation of scales is observed in the top and bottom left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.

>>>>

\subsection{Numerics}
\label{sct:numerics}
We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008} and safety factor 0.35.
All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
The aspect ratio of our domains is two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution of the bulk of the simulations in this work (see Appendix \ref{app:accelerated_evolution} for details).

The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.

In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.

\subsection{Dependence on $\mP$}
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{parameters_vs_p.pdf}
\caption{
Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (Left, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (Right, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}).
The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
The discontinuous penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
The discontinuous-gradient penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
We generally find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration depths.
In the bottom panels, we measure the evolved values of $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
\label{fig:parameters_vs_p}
}
\end{figure*}

We find that the depth of the penetration zone is strongly dependent on $\mP$.
In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.

The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that it is reasonable but imprecise to assume that $f$ and $\xi$ are constant as a function of $\mP$.
We find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
Most of the trend of $f$ increasing as $\mP$ decreases can be explained by slight increases in the CZ velocities and corresponding increases in the dissipation.
We speculate that, as $\mP$ decreases, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) more efficiently deflects convective velocities sideways before they have a chance to buoyantly break, thereby slightly increasing bulk-CZ velocities.
A similar trend of $\xi$ increasing as $\mP$ decreases can be seen.
This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
As the size of the PZ shrinks, dynamics do not have the space to change from their bulk-CZ properties, and so $\xi$ is closer to one.

@@

We find that the depth of the penetration zone is weakly dependent on $\mS$.
In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.

We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our turbulent cases.

@@

We find that the depth of the penetration zone is weakly dependent on $\mR$.
In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth $\delta_{0.5}$ with the Reynolds number.
In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
We find that $f$ increases with increases $\mR$, but is perhaps leveling off.
We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
Indeed, the variation of $\delp$ with $\mR$ can be seen as a variation of $\delp$ with $f$ in the bottom left panel.
We find that this is true both for simulations with stress-free dynamical boundary conditions (open symbols, SF) and for no-slip conditions (closed symbols, NS).

In order to understand this better, we note that the dissipation profile can reasonably be approximated as a constant value in the CZ and zero in the bottom viscous boundary layer.
We have visualized a NS dissipation profile in the right panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
This means that we can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
\begin{equation}
\int_{\rm{CZ}} \bar{\Phi} dz = C ( L_s - \delta_\nu ),
\end{equation}
where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
In other words, under this model, we expect the dissipation, and thus $f$, to vary linearly with the viscous boundary layer depth.
We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \propto \delta_\nu$ is a decent description for the SF simulations (NS simulations show an increase at small $\delta_\nu$, but also have maximized dissipation in the bounary layer).
In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
If you assume the Nusselt Number dependence on the Rayleigh number is Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$. 
The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.} \citep{ahlers_etal_2009, goluskin2016}.
Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $\delta_{0.5}$ to level off as $\mR$ increases to high values in the astrophysical regime.

Unfortunately, we are limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}), so we cannot extend our study to more turbulent simulations and higher values of $\mR$ than the ones shown here.
We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- suggest that PZ depths should saturate at high $\mR$.

@@

\section{Accelerated Evolution}
\label{app:accelerated_evolution}
As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure can be done accurately.
This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
This same separation of scales is observed in the left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
